\documentclass{myCV}

\addbibresource{publications.bib}
\addbibresource{presentations.bib}
\addbibresource{abstracts.bib}

\def\myName{Suk Hyun Sung}
\def\myAddress{2125 H. H. Dow Bldg.\\2300 Hayward St.\\Ann Arbor,MI 48109}
\def\myNumber{+1 (734) 263-7715}
\def\myEmail{sukhsung@umich.edu}
\def\myWebsite{shsung.com}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Education}
    \begin{entry}
        \textbf{MS/Ph.D (Materials Science \& Engineering)}, University of Michigan, Ann Arbor, MI \hfill Current\par
        \sbt{} Research Emphasis: Electron Microscopy, Low-dimension Materials, Quantum Materials.\par
    \end{entry}
    \begin{entry}
        \textbf{Bachelor of Science (Engineering Physics)}, Cornell University, Ithaca, NY \hfill Aug. 2012 -- Jan. 2016\par
        \sbt{} Study Emphasis: Solid State Physics, Materials Science\par
        \sbt{} Deans's List: Fall 2012, Fall 2013, Fall 2014, Spring 2015
    \end{entry}
    
%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Publications}
    \publication{yalisove2021abcorr}{}
    \publication{schnitzer2020strehl}{}
    \publication{meisenheimer2019magnetic}{}
    \publication{wang2019single}{}
    \publication{sung2019stacking}{}
    \publication{schnitzer2019ronchi}{}
    \publication{yoo2019atomic}{}
    \publication{chatterjee2016epitaxial}{}
    \publication{nie2014atomically}{}

    \begin{entry}
       \upAst{} The authors contributed equally
    \end{entry}
    \begin{entry}
       \upDag{} Corresponding Author
    \end{entry}
    
%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section*{Conference Abstracts}
    \abstracts{Absyalisovemm2019abCorr}{\upDdag{}}
    \abstracts{Absschnitzermm2019strehl}{}
    \abstracts{Absschnitzermm2018stacking}{\upDdag{}}
    \abstracts{AbsyooAPS2018tBLG}{}
    \abstracts{AbsengelkeAPS2018tBLG}{}
    \begin{entry}
      \upDdag{} First Authors Received M \& M Student Scholar Awards
    \end{entry}
%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Presentations}
    \conference{PressungAISTEM2021}{}
    \conference{Pressungmm2020tBLG}{}
    \conference{Presyalisovemm2020abCorr}{}
    \conference{Preshovdenmm2020abCorr}{}
    \conference{Presengelkemm2020tBLG}{}
    \conference{Preshovdenmm2020CDW}{}
    \conference{PresyalisoveFEMMAbcorr}{}
    \conference{Presyalisovemm2019abCorr}{\upDdag{}}
    \conference{Presschnitzermm2019strehl}{}
    \conference{Presschnitzermm2018stacking}{\upDdag{}}
            
    \begin{entry}
       \upAst{}The authors contributed equally
    \end{entry}
    
%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Research Experiences}
    \begin{entry}
        \textbf{Graduate Student Research Assistant}, Hovden Lab, University of Michigan \hfill Apr. 2016 -- Current\par
        Research Emphasis: 2D Materials, Quantum Materials
    \end{entry}
    \begin{entry}
        \textbf{Visiting Scientist}, Kourkoutis Electron Microscopy Group, Cornell University \hfill Jan. 2016 -- Jun 2016\par
        Research Emphasis: Nano-characterization of thin-film complex oxide heterostructure using scanning transmission electron microscopy (STEM), electron energy loss spectroscopy (EELS) and energy dispersive x-ray spectroscopy (EDS)\par
        \sbt{} Prepared epitaxially grown thin film YbAl3 on MgO substrate with LuAl3 and Al buffer into electron-transparently thin lamella using focused ion beam (FIB).\\
        \hspace{2em} Performed STEM and EDS to examine and confirm the epitaxial growth of the film and separation of the YbAl3 layer from the intermediate buffer layers.\\
        \hspace{2em} $[$Chatterjee, et al. Journal of Applied Physics, 120, 035105 (2016)$]$\par

        \sbt{} Examined epitaxially grown thin film Nd\textsubscript{0.5}Sr\textsubscript{0.5}MnO\textsubscript{3} on SrTiO\textsubscript{3} substrate the system was expected to show short-range A-site cation ordering behavior.\\
        Confirmed the presence of the ordering using Z-contrast HAADF-STEM and atomic resolution EELS data. The result is in preparation for submission.

    \end{entry}
    \begin{entry}
        \textbf{Undergraduate Researcher}, Kourkoutis Electron Microscopy Group \hfill Feb. 2014 -- Dec. 2015\par
        \sbt{} Preparation of electron-transparent (S)TEM specimen via tripod polishing technique\par
        \sbt{} Multislice simulation of STEM
    \end{entry}
    
%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Awards}
    \begin{entry}
        Dorothy \& Fred Chau Award: Excellence in Undergraduate Rsearch \hfill May. 2016
    \end{entry}
    \begin{entry}
        Engineering Learning Initiatives Undergraduate Research Award \hfill Apr. 2014 \& Sept. 2014
    \end{entry}
    
%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Skills}
    \begin{entry}
        Electron Microscopy: TEM, STEM, SEM, Multislice Simulations
    \end{entry}
    \begin{entry}
        Spectroscopy: Quantitative EELS and EDS
    \end{entry}
    \begin{entry}
        TEM Sample Preparation: Tripod Polishing, Focused Ion Beam
    \end{entry}
    \begin{entry}
        Software: MATLAB, Python, HTML/CSS/Javascript, C, ImageJ, Adobe Illustrator, Adobe Photoshop, Blender
    \end{entry}
    
%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Teaching Experiences}
    \begin{entry}
        \textbf{Graduate Student Instructor}, University of Michigan \hfill Aug. 2019 -- Dec. 2019\par
        \sbt{} Teaching assistant for `Intorudction to Electron Microscopy (MSE 562)'
    \end{entry}
    \begin{entry}
        \textbf{Undergraduate Teaching Assistant}, Cornell University \hfill Aug. 2015 -- Dec. 2015\par
        \sbt{} Assisted graduated TA for `Physics I: Mechanics and Heat (PHYS 1112)'
    \end{entry}
    \begin{entry}
        \textbf{Paid Tutor} \hfill Jun. 2012 -- Aug. 2017\par
        \sbt{} Tutored various high school/AP level mathematics and science courses
    \end{entry}

%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Reference}
    \begin{entry}
        Professor Robert Hovden \hfill University of Michigan, Ann Arbor, MI\\
        \hspace{2em} E-mail: hovden@umich.edu
    \end{entry}


\end{document}